{\Large \bf A Message From the Program Committee}
\bigskip\\

The Association for Computational Heresy Special Special Interest
Group (ACH SIGBOVIK) on Harry Q. Bovik's 6th Binarennial Workshop
about Symposium on Robot Dance Party of Conference in Celebration of
Harry Bovik's birthday has a rich and noble legacy. We, the current
members of the program committee were delighted to discover this
legacy as we \st{made it up} rooted through the files of the SIGBOVIK
Ministry of History, writing this introduction.

The first SIGBOVIK Conference was held on young Harry Bovik's first
birthday in 1942. It was a brief affair, as all of the attendees had
short, childish attentions spans. This has not changed. This was the
occasion of Fred Hacker's famous talk, {\it Waaaah: Want Bottle}. This
talk set a precedent for SIGBOVIK's level of discourse through the
years.

The SIGBOVIK Conference was not held on Harry's second and fourth
birthdays. These are known colloquially as the dark years. Harry was
going through a {\it phase} at the time. This phase went on for six
years. Even then, Harry had a long-term approach that would serve him
well in his research.

SIGBOVIK IV: BOVIKMANIA was a wild affair. Chuckles the Clown's
keynote was interrupted by what records describe only as {\em The Cake
Incident.} Records are unclear about the nature of this incident, but
we think it is safe to say it involved cake. This conference also
marked Harry Bovik and Fred Hacker's first public feud, signified by a
pair of position papers titled {\em Fred Hacker is a doodyhead} and
{\em Takes one to know one.}

The fifth SIGBOVIK symposium helped establish the conference as the
foremost venue for computer science research and Harry Bovik himself as
its brightest star, noted for his clever ideas and stunning seventies
wardrobe. Of the eighteen presenters, seventeen went on to win Turing
awards. The other was current Governor of California Arnold
Schwarzenegger. However, the spotlight was stolen by Harry himself who
submitted an astonishing thirty-two papers to the conference in honor
of his age. Each was a veritable oyster's pearl of
brilliance. Unfortunately, they were lost in an accident involving
three radishes, four peeled carrots, six celery sticks, and a
cuisinart machine. Demoralized, Harry never replicated those
results. Computer Science still has not recovered from this loss.

This brings us to up to date, ready for the sixth SIGBOVIK Conference
and Harry's sixty-fourth birthday. The minds behind this year's crop
of SIGBOVIK submissions are so bright, they wear sunglasses to
bed. We, on behalf of the SIGBOVIK Organizing Committee, are proud to
present this year's submissions.

\begin{center}
-The SIGBOVIK Committee For Writing An Introduction to the Proceedings
\end{center}
